### 2022-11-06 materials-lisa/notes/notes.tex
added data summary and graphs for projection data

\pagebreak
\section{Experiments with Conditionals}

	\subsection{1c---Conditional embedding,  are you sure?, assent + assertion of complement + Q-A judgment}
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Are you sure?
			\b. \textbf{Christopher:} Yes, I'm sure that Julian dances Salsa.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.85]{figures/c1-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. 1c}
			\label{fig:m1-corr}
		\end{figure}

	\subsection{2c---Conditional embedding yes, that's true+complement diagnostic (+ acceptability rating)} % (fold)
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Yes, that’s true, Julian dances salsa.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.85]{figures/c2-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. 2c}
			\label{fig:m1-corr}
		\end{figure}

	\subsection{3c---Conditional embedding, yes, that's true + negation of main clause (+ acceptability rating)} % (fold)
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Yes, that’s true, but Cole didn't discover it.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.85]{figures/c3-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. 3c}
			\label{fig:m1-corr}
		\end{figure}

\pagebreak
\section{To do} % (fold)

>>>>

\pagebreak
\section{Some more notes} % (fold)

	\subsection{At-issueness diagnostics} % (fold)

		\begin{itemize}
			\item some diagnostics of at-issueness for some propositions $p$, $q$ associated with $U$  may work fine for certain types of declaratives, based on
			\begin{itemize}
				\item whether $p, q$ are logically independent of each other
				\item if $p, q$ are both true according to speaker, if at-issueness of content can be diagnosed given the assumption that speaker is committed to content (or not)
			\end{itemize}

			\item because of point about commitment definitely does not work for at-issueness of content under entailment-cancelling operators (point about commitment)

			\item may run into problems for embedded / matrix content, because these are related, unlike e.g. appositives (but like evidentials)

	% subsection at_issueness_diagnostics (end)

% section some_more_notes (end)

\section{To do} % (fold)
